paper

### 2022-03-31 outputs/paper.Rmd
nothing much

```{r, echo = FALSE}
# number of employed women selected in the admiistrative regions
child %>% 
  filter(x == "number of employed women") %>% 
  ggplot(aes(x = x,
             y = percentage,
             fill = background)) +
  geom_bar(stat = 'identity',
           position = 'dodge') +
  labs(x = 'Administrative regions',
       y = 'Number of employed women') +
  theme_minimal() +
  scale_fill_brewer(palette = 'Set3') +
  theme(legend.position = "bottom")
```

>>>>

```{r, echo = FALSE}
# number of employed women selected in the administrative regions
child %>% 
  filter(x == "number of employed women") %>% 
  ggplot(aes(x = x,
             y = percentage,
             fill = background)) +
  geom_bar(stat = 'identity',
           position = 'dodge') +
  labs(x = 'Administrative regions',
       y = 'Number of employed women') +
  theme_minimal() +
  scale_fill_brewer(palette = 'Set3') +
  theme(legend.position = "bottom")
```
